---
title: "R Markdown and Leaflet"
author: "Andrew Stewart"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, results="hide", message=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "asis", fig.width=7, fig.height=7)
library(leaflet)
library(data.table)
library(dplyr)
library(knitr)
```
## Date: 10/28/2017
### Places and Stops From April RV-Vacation

This lesson requires:  
 - a webpage with a date (see above), and  
 - an interactive map created with `leaflet` (see below).  
  
The locations and link data in this map were orginally stored in `My Places` in `Google Earth`; recording the places we stopped in our RV Vaction in April 2017.  I imported `My Places` from a **.kmz** file to a **.csv** file that could be read by `R`.  The **.csv** file was edited with a reference to a **.png** file for `leaflet` to use as an `icon`.

Icon files were downloaded from from Google:  https://mapicons.mapsmarker.com/category/markers/

```{r Read Vacay Datafile, echo = TRUE, results = "markup"}

## Read activity.csv and format as tbl_df
vacayData <- read.csv("April Vacation Locations.csv", header = TRUE)
vacayData <- tbl_df(vacayData)

vacayLatLong <- vacayData[,1:2]
vacaySites <- vacayData[,"Link_URL"]
vacayNames <- vacayData[,"Name"]

vacayIcons <- iconList(makeIcon(paste(vacayData$icon_name),iconWidth=32, iconHeight=32))

vacayLatLong %>% leaflet(width = "100%") %>% addTiles() %>% addMarkers(~lng, ~lat, icon = vacayIcons, popup = vacaySites$Link_URL, clusterOptions = markerClusterOptions(zoomToBoundsOnClick = TRUE))
  
```
Hosted on GitHub     
      
Located at: https://adstewart91.github.io/R-Markdown-and-Leaflet/Leaflet_Assignment.html

RMarkDown: https://github.com/adstewart91/R-Markdown-and-Leaflet/blob/gh-pages/Leaflet%20Assignment.Rmd


          
